Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-11-21 revise/revise.tex
adds new text to solution

Other important works have been prepared in China in the frame of the Chinese MSR program.
\begin{solution}
        <++>
\end{solution}

@@

\end{questions}
  \end{document}

>>>>

Other important works have been prepared in China in the frame of the Chinese MSR program.
\begin{solution}
        Thank you for the excellent recommendations. The new text reads thus:

        Simulation tools developed by many authors successfully describe 
        steady-state and
        transient behavior of myriad MSR concepts. Krepel et al. extended 
        the in-house LWR
        diffusion code DYN3D to consider drift of delayed neutron precursors 
        alongside
        the reactor temperature profile, re-casting the extended code as
        DYN3D-MSR \cite{krepel_dyn3d-msr_2007}. That work compared DYN3D-MSR 
        against
        experimental MSRE data and then used it to simulate local fuel 
        channel
        blockages as well as local temperature perturbations.

        In a similar vein, Kophazi et. al. used iterative coupling between 
        in-house
        three-dimensional neutronic and one-dimensional heat conduction models 
        DALTON
        and THERM to analyze normal MSRE operation as well as
        channel-blocking-incident transients \cite{kophazi_development_2009}. 
        The
        Kophazi model added entrance effects of heat transfer coefficients as 
        well as
        thermal coupling between fuel channels through moderator heat 
        conduction. More
        recently, Cammi et. al. performed a 2D-axisymmetric single-channel 
        analysis of
        the MSBR using the commercial finite element package COMSOL 
        Multiphysics
        \cite{cammi_multi-physics_2011}. That work directly solved the fuel 
        salt
        velocity field, used heterogeneous group constants in fuel and 
        moderator
        regions, and employed the COMSOL software package intrinsically 
        designed
        for coupled multi-physics simulation.  Fiorina, Lathouwers, and their
        colleagues conducted a benchmarking exercise 
        \cite{fiorina_modelling_2013} in
        which this Politecnico di Milano approach was expanded to a 
        multi-channel model 
        of the MSFR and compared to code from the University of Delft
        \cite{de_zwaan_static_2007,van_der_linden_2012} based on the approach 
        in
        \cite{kophazi_development_2009}. These models showed good agreement for
        multiple accident transients. Meanwhile, leveraging lessons learned 
        from these 
        efforts has resulted in a multiscale approach from Zanetti et al. 
        \cite{zanetti_geometric_2015} successfully combines high and low 
        geometric 
        fidelity for graphite-moderated MSRs.

        More recently, Aufiero et.  al \cite{aufiero_development_2014} have 
        begun to
        approach transient simulations in the MSFR within the finite 
        volume
        OpenFOAM multiphysics toolkit\cite{weller_tensorial_1998}.  This 
        approach
        benefits from pre-implemented turbulence models available in the 
        OpenFOAM
        library and captures the full-core three-dimensional geometry of the 
        reactor
        primary circuit.  OpenFOAM CFD has additionally been shown by 
        Laureau et
        al. \cite{laureau_transient_2017} to couple well with Transient Fission 
        Matrix
        neutronics within the MSFR.
\end{solution}

@@

\end{questions}
\bibliographystyle{unsrt}
\bibliography{Moltres}
  \end{document}
